\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip

### 2015-03-05 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
Some fixes in bibliography
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64805 15284696-431f-4ddb-bdfa-cd5b030d7da7

A set of modules for multiscale analysis of landscape structure was added in 1992 
by Baker et al. \cite{baker1992r}, who developed the r.le model similar to 
FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
improved to become r.li in 2006. Further development continued, with a significant 
speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
The module v.surf.rst for spatial interpolation was developed approximately 12 years 
ago, since then it was improved several times (Trac2, 2014). It is an important part 
of GRASS GIS and is even taught at geospatial modeling courses, for example 
http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html.\vspace{5mm}\newline

>>>>

A set of modules for multiscale analysis of landscape structure was added in 1992 
by Baker et al., 1992 \cite{baker1992r}, who developed the r.le model similar to 
FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
improved to become r.li in 2006. Further development continued, with a significant 
speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
The module v.surf.rst for spatial interpolation was developed approximately 12 years 
ago, since then it was improved several times (Trac2, 2014). It is an important part 
of GRASS GIS and is even taught at geospatial modeling courses, for example 
http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html.\vspace{5mm}\newline
